Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-11-30 paper/reply.tex
added Preliminaries (R1)

@@

Some specific comments:
1) In (8), $\Delta_{q} G$ accounts for quantization errors, but I thought it was already account for in the additive disturbance $\nu$.

>>>>

\noindent \textbf{Preliminaries (R1)}

\noindent Since our stability analysis is based on polynomial coefficients
and not over signals, in Equation (8) $\Delta_{q} G$ is a model that incorporates 
the effects of $\nu$ in $\vec{\hat{G}}$, in order to investigate the system's 
stability consequences.

\noindent The $\Delta_{b}$ of a coefficient $c$ (represented by $\Delta_{b}c$) models 
the error in the fixed-point representation of $c$, which is the division remainder 
between the correct value of coefficient $c$ and its respective FWL format $\tilde{c}$, 
i.e., $\Delta_{b}c=c~ \texttt{mod}~\tilde{c}$.

@@

Some specific comments:

1) In (8), $\Delta_{q} G$ accounts for quantization errors, but I thought it was already account for in the additive disturbance $\nu$.
